Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-08 reports/manuscript.Rmd
Remove ORs and rerun pipeline
Fixes #23

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>

>>>>

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.

<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship.
Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].</span>
<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>

### 2023-03-08 reports/revision_letter.Rmd
Update dataset and rerun pipeline
Remove ORs and rerun pipeline
Fixes #23

Please see response to Reviewer 1, \Comment{r1_4}.

@@

\WorkInProgress
\todo{For linear - yeah, but this is always a problem in meta-analyses.
Need to think about ORs.}

@@

>>>>

Please see response to Reviewer 1, \Comment{r1_4}.
We agree that the use of causal langauge from an evidence-base that is mostly cross-sectional would be misleading.
We did not intend to make causal statements, and have reviewed the manuscript for any remaining instances.

@@

We agree that the relationship between some outcomes and screen time may not always be linear.
However, our previous research (e.g., 10.1186/s12966-019-0881-7) looking at a range of health and education outcomes in a high-quality dataset found little evidence for curvilinear relationships.
We therefore felt that the linear model was appropriate for the majority of the outcomes in this review.
Additionally, almost none of the reviews we included reported information that would allow us to calculate non-linear effects.
We agree that this is an important limitation though, and have added information on this to the *Discussion* section:

`r get_revision("r2_16")`

Regarding odds ratios, we initially included these based on several papers that suggested that a conversion to *r* was possible (e.g., 10.1037/0003-066X.62.3.254). 
On further consideration, we agree with the reviewer that it is difficult to ensure that this conversion produces comparable estimates when the categories used across studies is inconsistent.
We have therefore removed effect sizes calculated from odds ratios from our results.
In our efforts to remain completely transparent, these data remain available in the supplementary material.

@@

Per \comment{r2_16}, we decided not to include ORs in the meta-analyses.
